\textbf{Towards File System integrity verification in BTRFS}

### 2019-07-30 paper.tex
Move Conclusion section and add body.

\section{Conclusion}
TODO

@@

>>>>

@@

\section{Conclusion}
Thanks to BTRFS already using checksums for both data and meta-data, turning
it into an authenticated and verified File System is a technically feasible
task.  Using BTRFS instead of other File System or Block Layer level
mechanisms also provides advantages, like authenticated meta-data, as opposed
to fs-verity, or the ability to be able to alter the File System by a
legitimate administrator or user of the File System.
